---
title: "Data-Organization"
author: "Anna Talucci"
date: "11/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)
library(readr)
library(cowplot)

library(DT)
library(sf)
library(sp)
library(ggmap) # devtools::install_github("dkahle/ggmap")
library(ggrepel)
library(raster)
library(rgdal)
library(rasterVis)
library(RColorBrewer)
library(cowplot)
library(ggspatial)
library(maps)
library(RStoolbox)
library(mapproj)
library(magick)
```

# Individual data
```{r}
frost = read.csv("../data/2020-11-03_CSV/Frost_Permafrost_Data.csv")
odon = read.csv("../data/2020-11-03_CSV/ODonnell_Permafrost_Data.csv")
rocha = read.csv("../data/2020-11-03_CSV/Rocha_Permafrost_Data.csv")
verav = read.csv("../data/2020-11-03_CSV/Veraverbeke_Permafrost_Data.csv")
```


```{r}
str(frost)
```

```{r}
str(odon)
```

```{r}
str(rocha)
```

```{r}
str(verav)
```

# Data
```{r}
temp = list.files("../data/2020-11-03_CSV/", pattern="*.csv")
```


````{r}
tbl <-
    list.files("../data/2020-11-03_CSV",pattern = "*.csv") %>% 
    map_df(~read_csv(.))
```


```{r}

for (i in 1:length(temp)) assign(temp[i], read.csv(temp[i]))
```


```{r}
fs_path <- "../data/2020-11-03_CSV"   # path to the data
fs_files <- dir(fs_path, pattern = "*.csv") # get file names
fs_files
```

```{r}
fs_data <- fs_files %>%
  # read in all the files, appending the path before the filename
  map(~ read_csv(file.path(fs_path, .), .id = "file_name")) %>% 
  reduce(rbind)
fs_data
```
map_df(~read_csv(.x, col_types = cols(), col_names = FALSE), .id = "file_name")


```{r}
list_of_files <- list.files(path = "../data/2020-11-03_CSV",
                            full.names = TRUE)
list_of_files
df <- list_of_files %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x, col_types = cols(), col_names = TRUE), .id = "file_name")     
df
```

#Subsett data

```{r}
head(frost)
```

```{r}
frost1 = frost %>% dplyr::select(last_name:boreal_tundra, burn_unburn) %>% na.omit()
```

```{r}
odon1 = odon %>% dplyr::select(last_name:boreal_tundra, burn_unburn) %>% na.omit()
```

```{r}
rocha1 = rocha %>% dplyr::select(last_name:boreal_tundra, burn_unburn) %>% na.omit()
```

```{r}
verav1 = verav %>% dplyr::select(last_name:boreal_tundra, burn_unburn) %>% na.omit()
```

```{r}
fs_df = rbind(frost1, odon1, rocha1, verav1)
```

```{r}
summary(fs_df)
```


```{r eval=FALSE, include=FALSE}
write.csv(fs_df,"../outputs/2020-11-03_FS_data.csv", row.names = FALSE)
```

#  North Pole
```{r}
np = read.csv("../data/north_pole.csv")

```
# Projections

## WGS 84
WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

## Russia EE Area
Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 
+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 "
```


##Polar
+proj=stere +lat_0=90 +lat_ts=71 +lon_0=0 +k=1 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs 

```{r}
polar = "+proj=stere +lat_0=90 +lat_ts=71 +lon_0=0 +k=1 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs "
```

# BBOX

```{r}
coords_arctic = matrix(c(-180.0, 90.0,
               180.0, 90.0,
               180.0, 60.0, 
               -180.0, 60.0), 
             ncol = 2, byrow = TRUE)
```

```{r}
arctic_coord = Polygon(coords_arctic)
arctic_poly = SpatialPolygons(list(Polygons(list(arctic_coord), ID = "a")), proj4string=CRS(wgs_proj))
```

```{r}
plot(arctic_poly, axes = TRUE)
```

#Create spatial points data frame with attributes
## PCN data 
Define Lat/Long
```{r}
coords_fs = cbind(fs_df$long, fs_df$lat)

fs_df_pt <- SpatialPointsDataFrame(coords_fs, proj4string = CRS(wgs_proj), data = fs_df)
```

Transform to Equal area projection
```{r}
fs_df_polar <- spTransform(fs_df_pt, CRS(polar))
```

```{r}
fs_df_polar_sf = st_as_sf(fs_df_polar)
```


```{r}
st_write(fs_df_polar_sf, "../outputs/fs_df_polar_sf.shp", driver="ESRI Shapefile") 
```
##NP
Define Lat/Long
```{r}
coords_np = cbind(np$long, np$lat)

np_pt <- SpatialPointsDataFrame(coords_np, proj4string = CRS(wgs_proj), data = np)
```

Transform to polar projection
```{r}
np_polar <- spTransform(np_pt, CRS(polar))
```

```{r}
np_polar_sf = st_as_sf(np_polar)
```

```{r}
buf <- st_buffer(geom, dist = 2500000)
```

```{r}
plot(np_polar_sf)
plot(buf, add=TRUE)
```

## World 

```{r}
library("rnaturalearth")
library("rnaturalearthdata")

world1 <- ne_countries(scale = "medium", returnclass = "sf")
class(world1)
world1
```





```{r}
world1_crop = st_crop(world1, xmin = -180, ymin = 45, xmax = 180, ymax = 83)
```

```{r}
plot(world1_crop)
```

```{r}
world1_crop_polar = st_transform(world1_crop, CRS(polar))

```

```{r}
ggplot() +
geom_sf(data = world1_crop_polar) 
```

# Permafrost
```{r}
permafrost = st_read("../data/permafrost/permaice.shp", "permaice")
```

```{r}
pf_polar_select = st_read("../data/permafrost/permafrost_polar_select.shp", "permafrost_polar_select")
```

```{r}
permafrost_wgs = st_transform(permafrost, CRS(wgs_proj))
permafrost_wgs
```



```{r}
pf_wgs_extent = permafrost_wgs %>% dplyr::select(EXTENT) %>% na.omit()
```


```{r}
ggplot() +
geom_sf(data = pf_wgs_extent) 
```

```{r}
permafrost_polar = st_transform(permafrost, CRS(polar))
permafrost_polar
```


```{r}
st_write(permafrost_polar, "../outputs/permafrost_polar.shp", driver="ESRI Shapefile") 
```

```{r}
plot(permafrost_polar)
```
```{r}
head(permafrost_polar)
summary(permafrost_polar)
```



## select variable to map
```{r}
pf_polar_extent = permafrost_polar %>% dplyr::select(EXTENT) %>% na.omit()
head(pf_polar_extent)
```

```{r}
pf_polar_select_ext = pf_polar_select %>% dplyr::select(EXTENT) %>% na.omit()
```
FID = c(8842, 4247, 2883, 6161 )

```{r}
pf_polar_extent_clip = pf_polar_extent %>% filter(st_contains(world1_crop_polar, ., sparse = FALSE))
```

```{r}
pf_polar_numcode = permafrost_polar %>% dplyr::select(NUM_CODE)
```

```{r}
fs_burn = fs_df_polar_sf %>% dplyr::select(burn_unburn)
```


```{r}
# Defines the x axes required
x_lines <- seq(-120,180, by = 60)
```

['#f6eff7','#bdc9e1','#67a9cf','#1c9099','#016c59']
```{r}
ggplot() +
geom_sf(data = world1_crop_polar, fill = "grey", color = "grey", alpha = 0.8) +
  geom_sf(data = pf_polar_select_ext, aes(fill = EXTENT, color = EXTENT)) +
    scale_fill_manual(values = c("S" = '#f6eff7', 'I' = '#bdc9e1','D' = '#67a9cf','C' = '#1c9099')) +
    scale_color_manual(values = c("S" = '#f6eff7', 'I' = '#bdc9e1','D' = '#67a9cf','C' = '#1c9099')) +
  # Convert to polar coordinates
  coord_map("ortho", orientation = c(90, 0, 0), xlim = c(-180, 180), ylim = c(70, 90)) +


  geom_sf(data = fs_burn, size = 2) +
  
  # Removes Axes and labels
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  xlab("") + 
  ylab("") +
  theme_bw() +
  theme(panel.background = element_rect(color = NA))



```


```{r}
# Defines the x axes required
x_lines <- seq(-120,180, by = 60)

map1 = ggplot() +
  geom_polygon(data = world1_crop_polar, aes(x = long, y = lat), fill = "wheat", colour = "black", alpha = 0.8) +
  coord_map("ortho", orientation = c(90, 0, 0)) +
  scale_y_continuous(breaks = seq(45, 90, by = 10), labels = NULL) +
  # Removes Axes and labels
  scale_x_continuous(breaks = NULL) +
  xlab("") + 
  ylab("") +
  # Adds labels
  geom_text(aes(x = 0, y = seq(55, 85, by = 10), hjust = -0.2, label = paste0(seq(55, 85, by = 10), "°N"))) +
  geom_text(aes(x = x_lines, y = 44, label = c("120°W", "60°W", "0°", "60°E", "120°E", "180°W"))) +
  # Adds axes
  geom_hline(aes(yintercept = 45), size = 1)  +
  geom_segment(aes(y = 45, yend = 90, x = x_lines, xend = x_lines), linetype = "dashed") +
# Change theme to remove axes and ticks
  theme(panel.background = element_blank(),
      panel.grid.major = element_line(size = 0.25, linetype = 'dashed',
                                      colour = "black"),
      axis.ticks=element_blank())


map1
  
```
  
# World
https://ggplot2-book.org/coord.html
